### 2019-01-02 arxiv/comparison.tex
Updated table accoriding to David comments, added acknowledgement section

		\midrule				
		& \multirow{5}{*}{A Train Full?}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A ?    &  98.8   \\
		\cmidrule{6-7} 
		TbD + reg &   &    &   &    & B ?    &  75.4   \\
		\cmidrule{4-5}\cmidrule{6-7}
		(\cite{mascharka2018transparency}) &  &    & \multirow{2}{*}{B Valid 30k}  & \multirow{2}{*}{N/A}     & A ?    &  96.9 \\
		\cmidrule{6-7} 
		&   &    &   &    & B ?   &  96.3  \\

@@

They also compare their performance on CoGenT against PG+EE.
Nonetheless, the description lacks information about the used sets for training, fine-tuning and testing. 
They indicate that they used 3k images and 30k questions from the CoGenT Condition B for fine-tuning of their model, but do not explicitly point the set they used the samples from.

>>>>

		\midrule				
		& \multirow{5}{*}{A Train Full}   & \multirow{5}{*}{N/A}  & \multirow{2}{*}{--} & \multirow{2}{*}{--}  &   A Test Full    &  98.8   \\
		\cmidrule{6-7} 
		TbD + reg &   &    &   &    & B Test Full    &  75.4   \\
		\cmidrule{4-5}\cmidrule{6-7}
		(\cite{mascharka2018transparency}) &  &    & \multirow{2}{*}{B Valid 30k}  & \multirow{2}{*}{N/A}     & A Test Full    &  96.9 \\
		\cmidrule{6-7} 
		&   &    &   &    & B Test Full   &  96.3  \\

@@

They also compare their performance on CoGenT against PG+EE.
The authors (in a separate conversation) explained that they trained their models on Condition A training set and tested on Condition A and Condition B test sets respectively.
For fine-tuning on CoGenT-B the authors used the first 3k images (Val-B indices 0-2999) in the CoGenT-B validation dataset and all of their corresponding questions.

They indicate that they used 3k images and 30k questions from the CoGenT Condition B for fine-tuning of their model, but do not explicitly point the set they used the samples from.
